Formalizing Stack Safety as a Security Property\ifcameraready\else\vspace{-0.75cm}\fi

### 2023-05-24 submission5/core.tex
Proofreading

  \judgmentbr{\(\components = \mathit{range} ~ \SP ~ \mathit{off} ~ \mathit{sz} ~ \mach \cap \unsealed(V)\)}
             {\(V' = V \llbracket \addr \mapsto \object \mid \addr \in \components \rrbracket\)}
             {\(Op ~ \mach ~ (\mathbf{alloc} ~ \mathit{off, sz}) ~ (V,\sigma) = (V',\sigma)\)}
    %
    \judgmentbr{\(\components = \mathit{range}~ \SP ~ \mathit{off} ~ \mathit {sz} ~ \mach \cap \object(V)\)}
               {\(V' = V \llbracket \addr \mapsto \unsealed \mid \addr \in \components \rrbracket\)}
               {\(Op ~ \mach ~ (\mathbf{dealloc} ~ \mathit{off, sz}) ~ (V,\sigma) = (V',\sigma)\)}
    %
    \judgment{\(V' = \lambda \component .
      \begin{cases}
        \unsealed & \textnormal{if } k \in CLR \\
        \public & \textnormal{if } k \in \overline{\reg_{\mathit{args}}} \\
        \sealed & \textnormal{if } k \in \WORDS \textnormal{ and } k \in \object(V') \\
        V(k) & \textnormal{otherwise} \\
      \end{cases}\)}
             {\(Op ~ \mach ~ (\mathbf{call} ~ \addr_{target} ~ \overline{\reg_{args}})
               ~ (V,\sigma) = (V',V::\sigma)\)}
    %
    \judgment{}
             {\(Op ~ \mach ~ \mathbf{return} ~ (\_, (V,\sigma')) = (V, \sigma')\)}
             \caption{Basic Operations}
  \label{fig:basicops}
\end{figure}

@@

    \vspace{\abovedisplayskip}
    \judgmentthree[\sc Tailcall]
        {\(\components = \mathit{passed} ~ \overline{sa} ~ \cup ~ \overline{\reg_{args}}\)}
        {\(\components' = \mathit{reach}^* ~ \components ~ \rho\)}
        {\(V' = \mathit{push} ~ V ~ \overline{\reg_{args}} ~ K'\)}
        {\(Op ~ \mach ~ (\mathbf{call} ~ \addr_{\mathit{target}} ~ \overline{\reg_{args}} ~ \overline{sa}) ~ (V,\sigma,\rho) = (V',V::\sigma,\rho)\)}

>>>>

  \judgmentbr{\(\components = \mathit{range} ~ \SP ~ \mathit{off} ~ \mathit{sz} ~ \mach \cap \unsealed(V)\)}
             {\(V' = V \llbracket \addr \mapsto \object \mid \addr \in \components \rrbracket\)}
             {\(Op ~ \mach ~ (\mathbf{alloc} ~ \mathit{off, sz}) ~ (V,\sigma) = (V',\sigma)\)}
    %
    \judgmentbr{\(\components = \mathit{range}~ \SP ~ \mathit{off} ~ \mathit {sz} ~ \mach \cap \object(V)\)}
               {\(V' = V \llbracket \addr \mapsto \unsealed \mid \addr \in \components \rrbracket\)}
               {\(Op ~ \mach ~ (\mathbf{dealloc} ~ \mathit{off, sz}) ~ (V,\sigma) = (V',\sigma)\)}
    %
    \judgment{\(V' = \lambda \component .
      \begin{cases}
        \unsealed & \textnormal{if } k \in CLR \\
        \public & \textnormal{if } k \in \overline{\reg_{\mathit{args}}} \\
        \sealed & \textnormal{if } k \in \WORDS \textnormal{ and } k \in \object(V) \\
        V(k) & \textnormal{otherwise} \\
      \end{cases}\)}
             {\(Op ~ \mach ~ (\mathbf{call} ~ \addr_{target} ~ \overline{\reg_{args}})
               ~ (V,\sigma) = (V',V::\sigma)\)}
    %
    \judgment{}
             {\(Op ~ \mach ~ \mathbf{return} ~ (\_, (V,\sigma')) = (V, \sigma')\)}
             \caption{Basic Operations}
  \label{fig:basicops}
\end{figure}

@@

    \vspace{\abovedisplayskip}
    \judgmentthree[\sc Tailcall]
        {\(\components = \mathit{passed} ~ \overline{sa} ~ \cup ~ \overline{\reg_{args}}\)}
        {\(\components' = \mathit{reach}^* ~ \components ~ \rho\)}
        {\(V' = \mathit{push} ~ V ~ \overline{\reg_{args}} ~ K'\)}
        {\(Op ~ \mach ~ (\mathbf{call} ~ \addr_{\mathit{target}} ~ \overline{\reg_{args}} ~ \overline{sa}) ~ (V,\sigma,\rho) = (V',\sigma,\rho)\)}
